Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-06-07 manuscript.Rmd
cite replication crisis

A successful prediction should lend more credibility to a theory than a postdiction, all else equal.
The scientific community has long pondered the vital distinction between exploration and confirmation, discovery and justification, hypothesis-generating and hypothesis-testing and so forth [see @hoyningen-hueneContextDiscoveryContext2006].
Many researchers preregister their studies [@nosekPreregistrationRevolution2018] to honour this distinction and produce results that are considered confirmatory.
Indeed, rigorous application of preregistration prevents researchers from reporting a simple confirmatory story for a set of results produced by an arduous process of trial and error [@wagenmakersAgendaPurelyConfirmatory2012].
However, while many researchers intuitively recognize this as an advantage of preregistration, some remain unconvinced.
These skeptics question why a study should be preregistered at all.
Even researchers convinced of the advantages of preregistration face difficult problems when they exclusively rely on an intuitive appeal.
Specifially, an intuitive convinction is unable to address pragmatic questions, such as what to include, in how much detail in the preregistration, or about the conditions that warrant deviating from it.
If the research community remains confused about the purpose of preregistration, it is bound to misapply it and hence decrease the efficiency of the scientific endeavour. 
We thus propose a principled justification for preregistration with a formal objective against which researchers can evaluate several pragmatic trade-offs.

The scientific community asserts that the objective of preregistration is to distinguish confirmatory from exploratory research [@mellorEasyPreregistrationWill2018; @nosekPreregistrationRevolution2018; @wagenmakersAgendaPurelyConfirmatory2012].
Taken at face value, this objective implies that research is confirmatory if, and only if, it is preregistered.
However, this postulate not warrented.
Researchers can conduct confirmatory research without preregisteration.
Weather they can convince other researchers of the confirmatory nature of their research is a separate issue.
Preregistered but not strictly confirmatory studies are also commonplace.
Researchers may apply two strategies to evade the self-imposed restrictions of preregistrations.
One strategy is to write a loose preregistration, to begin with; another is to deviate from the preregistration afterwards.
Both strategies may be used with compelling scientific reasoning or with the self-serving intent of generating desirable results no matter the nature of the phenomenon under study.
Insisting on equating preregistration and confirmation has, hence, led to criticism that preregistration is actually negative sum, and neither sufficient nor necessary to establish confirmation [@szollosiPreregistrationWorthwhile2020; @phamPreregistrationNeitherSufficient2021]

>>>>

A successful prediction should lend more credibility to a theory than a postdiction, all else equal.
The scientific community has long pondered the vital distinction between exploration and confirmation, discovery and justification, hypothesis-generating and hypothesis-testing and so forth [see @hoyningen-hueneContextDiscoveryContext2006].
Confusing exploratory findings with confirmed theories has lead to a crisis of confidence of in the results of empirical sciences [@ioannidisWhyMostPublished2005] and psychology in particular [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
As a response, more and more researchers preregister their studies [@nosekPreregistrationRevolution2018] to honour this distinction and produce results that are considered confirmatory.
Indeed, rigorous application of preregistration prevents researchers from reporting a simple confirmatory story for a set of results produced by an arduous process of trial and error [@wagenmakersAgendaPurelyConfirmatory2012].
However, while many researchers intuitively recognize this as an advantage of preregistration, some remain unconvinced.
These skeptics question why a study should be preregistered at all.
Even researchers convinced of the advantages of preregistration face difficult problems when they exclusively rely on an intuitive appeal.
Specifially, an intuitive convinction is unable to address pragmatic questions, such as what to include, in how much detail in the preregistration, or about the conditions that warrant deviating from it.
If the research community remains confused about the purpose of preregistration, it is bound to misapply it and hence decrease the efficiency of the scientific endeavour. 
We thus propose a principled justification for preregistration with a formal objective against which researchers can evaluate several pragmatic trade-offs.

The scientific community asserts that the objective of preregistration is to distinguish confirmatory from exploratory research [@mellorEasyPreregistrationWill2018; @nosekPreregistrationRevolution2018; @wagenmakersAgendaPurelyConfirmatory2012].
Taken at face value, this objective implies that research is confirmatory if, and only if, it is preregistered.
However, this postulate is not warrented.
Researchers can conduct confirmatory research without preregisteration.
Convincing other researchers of the confirmatory nature of their research is a separate issue.
Preregistered but not strictly confirmatory studies are also commonplace.
Researchers may apply two strategies to evade the self-imposed restrictions of preregistrations.
One strategy is to write a loose preregistration, to begin with; another is to deviate from the preregistration afterwards.
Both strategies may be used with compelling scientific reasoning or with the self-serving intent of generating desirable results no matter the nature of the phenomenon under study.
Insisting on equating preregistration and confirmation has, hence, led to criticism that preregistration is actually negative sum, and neither sufficient nor necessary to establish confirmation [@szollosiPreregistrationWorthwhile2020; @phamPreregistrationNeitherSufficient2021]
